Abstraction and Invariance for Algebraically Indexed Types

### 2012-07-09 paper/section-general-framework.tex
Remove a fixme
minor changes
Add a label on the semantic equality definition

We use the relational interpretation to define semantic equivalence,
which is a sound approximation of contextual equivalence, as a
consequence of \thmref{thm:abstraction}.
\begin{definition}
  Let $\Gamma_{\mathit{ops}}$ and $\eta_{\mathit{ops}}$ be a context
  of primitive operations and its interpretation as in
  \defref{defn:ctxt-equiv}. Let $\relEnv{E}_{\mathit{ops}}$ be a
  substitutive family of sets of relational environments such that for
  all $\Delta$ and $\rho \in \relEnv{E}_{\mathit{ops}}(\Delta)$,
  $(\eta_{\mathit{ops}}, \eta_{\mathit{ops}}) \in
  \rsem{\Gamma}{\relEnv{E}_{\mathit{ops}}}\rho$.

@@

To satisfy the hypothesis of \thmref{thm:abstraction} we still need to
prove, for each instantiation of our general framework, that the
program-level primitive operations preserve all the relations.
\fixme{This is the content of lemma X, lemma Y, lemma Z, below}.

>>>>

We use the relational interpretation to define semantic equivalence,
which is a sound approximation of contextual equivalence, as a
consequence of \thmref{thm:abstraction}.
\begin{definition}\label{def:semantic-equality}
  Let $\Gamma_{\mathit{ops}}$ and $\eta_{\mathit{ops}}$ be a context
  of primitive operations and its interpretation as in
  \defref{defn:ctxt-equiv}. Let $\relEnv{E}_{\mathit{ops}}$ be a
  substitutive family of sets of relational environments such that for
  all $\Delta$ and $\rho \in \relEnv{E}_{\mathit{ops}}(\Delta)$,
  $(\eta_{\mathit{ops}}, \eta_{\mathit{ops}}) \in
  \rsem{\Gamma}{\relEnv{E}_{\mathit{ops}}}\rho$.

@@

To satisfy the hypothesis of \thmref{thm:abstraction} we still need to
prove, for each instantiation of our general framework, that the
program-level primitive operations preserve all the relations. This is
the content of \lemref{lem:geom-environments},
\lemref{lem:monoid-ops-related},
\lemref{lem:environments-information-flow} and
\lemref{lem:metric-environments}.
